Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-04-03 article.tex
Redefined time slice boundaries in section 3.3.4
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1490 ccdd05d5-56c1-461a-bf98-85f6876523b4

If the cost of the basis filters dominates, and the frequency of the templates
evolves slowly enough in time, then we can use the time-frequency relationship
of equation~(\ref{eq:fgw}) to estimate the speedup relative to the conventional, direct
\TD\ method.  The reduction in \flops\ is approximately
%
\begin{multline}
\label{eq:speedup}
\frac{2 \sum_{s=0}^{S-1} f^s \numsvdtmps \slicessamps}{2 \numtmps \tmpsamps f^0} \\
\approx \frac{\alpha}{\left(t_\mathrm{low} - t_\mathrm{high}\right) \left(f^0\right)^2} \int_{t_\mathrm{low}}^{t_\mathrm{high}} \left(2 f(t) \right)^2 \, \mathrm{d} t \\
= \frac{16 \alpha \left(t_\mathrm{low} f^2 (t_\mathrm{low}) - t_\mathrm{high} f^2 (t_\mathrm{high}) \right)}{\left(f^0\right)^2 \left(t_\mathrm{low} - t_\mathrm{high}\right)}
\end{multline}
%
where $\alpha \approx \numsvdtmps / \numtmps$ is the rank reduction factor, or
ratio between the number of basis templates and the number of templates.  This
approximation assumes that the frequency of the signal is evolving very slowly
so that we can approximate the time slice sample rate as twice the instantaneous
gravitational wave frequency, $f^s \approx 2 f(t)$, and the number of samples in
the decimated time slice as the sample rate times an infinitesimally short time
interval, $\slicessamps \approx 2 f(t) \, \mathrm{d}t$. The integral is
evaluated using the power-law form of $f(t)$ from equation~(\ref{eq:fgw}).
Substituting approximate values for a template bank designed for component
masses around (1.4, 1.4) $M_\odot$, $\alpha \approx 10^{-2}$, $t_\mathrm{low} = 10^3$~s,
$f_\mathrm{low} = 10^1$~Hz, $t_\mathrm{high} = 1/1570$~s, $f_\mathrm{high} = 1570$~Hz,
and $f^0 = (2)(1570)$~Hz, we find from equation~(\ref{eq:speedup}) that the
\lloid\ method requires only $\sim 10^{-6}$ times as many \flops\ as the
conventional \TD\ method.

>>>>

If the cost of the basis filters dominates, and the frequency of the templates
evolves slowly enough in time, then we can use the time-frequency relationship
of equation~(\ref{eq:fgw}) to estimate the speedup relative to the conventional, direct
\TD\ method.  The reduction in \flops\ is approximately
%
\begin{multline}
\label{eq:speedup}
\frac{2 \sum_{s=0}^{S-1} f^s \numsvdtmps \slicessamps}{2 \numtmps \tmpsamps f^0} \\
\approx \frac{\alpha}{\left(t_\mathrm{low} - t_\mathrm{high}\right) \left(f^0\right)^2} \int_{t_\mathrm{low}}^{t_\mathrm{high}} \left(2 f(t) \right)^2 \, \mathrm{d} t \\
= \frac{16 \alpha \left(t_\mathrm{low} f^2 (t_\mathrm{low}) - t_\mathrm{high} f^2 (t_\mathrm{high}) \right)}{\left(f^0\right)^2 \left(t_\mathrm{low} - t_\mathrm{high}\right)}
\end{multline}
%
where $\alpha \approx \numsvdtmps / \numtmps$ is the rank reduction factor, or
ratio between the number of basis templates and the number of templates.  This
approximation assumes that the frequency of the signal is evolving very slowly
so that we can approximate the time slice sample rate as twice the instantaneous
gravitational wave frequency, $f^s \approx 2 f(t)$, and the number of samples in
the decimated time slice as the sample rate times an infinitesimally short time
interval, $\slicessamps \approx 2 f(t) \, \mathrm{d}t$. The integral is
evaluated using the power-law form of $f(t)$ from equation~(\ref{eq:fgw}).
Substituting approximate values for a template bank designed for component
masses around (1.4, 1.4) $M_\odot$, $\alpha \approx 10^{-2}$, $t_\mathrm{low} = 10^3$~s, $f_\mathrm{low} = 10^1$~Hz, $f_\mathrm{high} = f_\mathrm{ISCO} \approx 1570$~Hz, $f^0 = 2 f_\mathrm{ISCO}$, and $t_\mathrm{high} = {f_\mathrm{ISCO}}^{-1}$, we find from equation~(\ref{eq:speedup}) that the
\lloid\ method requires only $\sim 10^{-6}$ times as many \flops\ as the
conventional \TD\ method.
